A geo-referenced micro-data set of real estate listings for Spain’s three largest cities

### 2022-08-12 editorial-materials/EPB-2022-0116_response_to_reviewer.Rmd

>3.	The method of randomisation is described but it would be advantageous to publish the code for this so that researchers can evaluate the impact of this kind of randomisation on this and other data sets. Does the method, as seems likely, have a differential effect on data from high density areas as compared with low?
To what extent are analyses likely to be confined to neighbourhood levels of resolution given the method of spatial randomisation? It would be useful to have some idea of the size of the neighbourhoods to facilitate comparison with other spatial data sets

The possible advese effects due to mislocation assets after coordinate randomisation is mitigated by the imposition of a boundary constraint in the relocation process. This constraint keeps the listing in the same neighborhood it belonged before relocation. For the process clarity sake we released the anonymization process in the R package code on github. [microsite](https://paezha.github.io/idealista18/anonymization)

>4.	More details on the data collection methods of Idealista would be useful in interpreting the data. Does Idealista concentrate on particular market segments or not? Are the list prices good indicators of actual sale prices? Are there sources from which actual paid prices could be identified?

Idealista covers fairly well all segments in the Spanish market, both individual and professional advertisers. This dataset comprehends information about listing prices, thus it contains the market situation from the offer.

@@

The main real estate portals in Spain are idealista and Fotocasa, further away are Habitaclia and Milanuncios, the latter focusing almost exclusively on private individuals. In September 2021, according to data from Similarweb (a site specialized in sites' traffic volume comparison), in Spain, there were a total of 103 million page views on real estate portals, out of page views on real estate portals, of which the four main portals, idealista, Fotocasa, Habitaclia, and Pisos.com, in that order, accounted for 94% of the traffic.

Another relevant feature of this sector is that it is highly concentrated, idealista being the leader by far with 58.6 monthly million visits (57% of the total traffic)  versus its immediate competitor with 19.9 million visits (19.3 % of total traffic). In terms of the evolution over time of interest in the content of each portal, based on data from Google Trends, the leadership of idealista Trends, the leadership of idealista has been shared from 2004 to 2015, subsequently consolidating idealista as the leader by a wide margin.

>5.	It would be useful for the authors to evaluate the datasets in the light of the FAIR guiding principles for research data stewardship (findability, accessibility, interoperability, and reusability).

We discuss our efforts to comply with FAIR guiding principles in the data description of the revised paper.

### 2022-08-12 EPB/EPB.Rmd
Updated license in repository and website and discussed FAIR guiding principles in paper

We are also witnessing a growing interest in open data in geography and data science [@arribasl2021editorial; @arribas2021]  using reproducible or replicable  research  [@paez2021open].  But  to  work  openly in  science, it  is  necessary to  have  free software and open data. While great efforts have been made to make free software available to researchers (e.g., R or Python), not much data is currently out in the open. In the particular case of the real estate market, to our knowledge, there are few open micro-data sets of housing markets available [@Song2021].

To overcome these limitations, this paper presents a sort description of an open micro-data set of geo-referenced dwelling listings. The data have been provided by the Idealista company\footnote{Idealista is the major real estate listing website in Spain, and present in other southern european countries as Italy and Portugal} and contain information about 189,923 dwellings located in Spain’s three largest cities. To date, this data product is the biggest open geo-referenced micro-data set of the housing market in Spain. Moreover, the data set has been supplied directly by Idealista, and therefore is clean and free of download errors. The listings have been enriched with official information from the Spanish cadastre along with other relevant geographical features, such as distance to urban points of interest. The data set is distributed as an R package, named ‘idealista18’, which can be accessed from the Github repository\footnote{The direct URL to the GitHub repository is \url{https://github.com/paezha/idealista18}}.

@@

The open data set ‘idealista18’ is an R package composed of nine objects, three objects for each of the three main Spanish cities: Barcelona, Madrid, and Valencia. For each city, dwelling listings, neighborhood polygons, and a set of points of interest have been included in the R package. The following subsections describe each object. A full description of the data is available in the help section of the package.

>>>>

We are also witnessing a growing interest in open data in geography and data science [@arribasl2021editorial; @arribas2021] using reproducible or replicable  research  [@paez2021open; @brunsdon2021opening]. But  to  work  openly in  science, it  is  necessary to  have  free software and open data. While great efforts have been made to make free software available to researchers (e.g., R or Python), data regarding real estate markets tend to be treated as confidential, and there are still few open micro-data sets of housing markets available [@Song2021].

To contribute to the growing inventory of international micro-data sets of real estate markets, this paper introduces an open micro-data set of geo-referenced dwelling listings. The data have been provided by the Idealista company\footnote{Idealista is the major real estate listing website in Spain, and present in other southern european countries as Italy and Portugal} and contain information about 189,923 dwellings located in Spain’s three largest cities. To date, this data product is the biggest open geo-referenced micro-data set of the housing market in Spain. Moreover, the data set has been supplied directly by Idealista, and therefore is clean and free of download errors. However, in order to be able to share publicly the data we have slightly modified some variables by applying some random noise which will not bias the main results derived from its usage.

This micro-data set is expected to be used as a benchmark dataset to test empirical methods in a reproducible fashion. Applied and theoretical researchers on real estate mass appraisal and valuation methods might use this dataset to canonically compare the performance of their proposed comparable and hedonic models, among others. The data can also be used to study the segmentation of housing submarkets and related topics such as the impact of suburban areas on house prices. The listings have been enriched with official information from the Spanish cadastre along with other relevant geographical features, such as distance to urban points of interest. In any case, the data might be easily extended by spatially joining other datasets that contain information at administrative, census tract, or postal code levels.

The data set is distributed as an R package, name {idealista18}, which can be accessed from a public Github repository\footnote{The direct URL to the GitHub repository is \url{https://github.com/paezha/idealista18}}. The open data product {idealista18} is made available under the \href{http://opendatacommons.org/licenses/odbl/1.0/}{Open Database License}. For transparency, we also share the randomisation process applied to the original data in the aforementioned Github repository.

@@

The open data product {idealista18} is an R package composed of nine objects, three objects for each of the three main Spanish cities: Barcelona, Madrid, and Valencia. For each city, dwelling listings, neighborhood polygons, and a set of points of interest have been included in the R package. The following subsections describe each object. A full description of the data is available in the help section of the package. We have strived to the best of our ability to comply with FAIR principles regarding research data [@Wilkinson2016fair]: upon publication, the dataset has a persistent digital object identifier; publication as a data article makes the data findable; the data and metadata are packaged together and protocols for help files in the R ecosystem mean that documentation is easily searchable; distribution as an R package means that only open software is needed to access the data; and a public repository documents all data processes followed to generate the distributed open data product.

### 2022-08-12 EPB/main_EPB.Rmd
Updated license in repository and website and discussed FAIR guiding principles in paper

---
title: A geo-referenced micro-data set of real estate listings for Spain’s three largest cities
runninghead: Rey-Blanco \emph{et al}.
author:
- name: 
abstract: "This article shares an open data product with big geo-referenced micro-data sets of 2018 real estate listings in Spain. These data were originally published on the idealista.com real estate website. The observations were obtained for the three largest cities in Spain: Madrid (n = 94,815 observations), Barcelona (n = 61,486 observations), and Valencia (n = 33,622 observations). The data sets include the coordinates of properties (latitude and longitude), asking prices of each listed dwelling, and several variables of indoor characteristics. The listings were enriched with official information from the Spanish cadastre (e.g., building material quality) plus other relevant geographical features, such as distance to urban points of interest. Along with the real estate listings, the data product also includes neighborhood boundaries for each city. The data product is offered as a fully documented R package and is available for scientific and educational purposes, particularly for geo-spatial studies"

@@

We are also witnessing a growing interest in open data in geography and data science [@arribasl2021editorial; @arribas2021]  using reproducible or replicable  research  [@paez2021open].  But  to  work  openly in  science, it  is  necessary to  have  free software and open data. While great efforts have been made to make free software available to researchers (e.g., R or Python), not much data is currently out in the open. In the particular case of the real estate market, to our knowledge, there are few open micro-data sets of housing markets available [@Song2021].

To overcome these limitations, this paper presents a sort description of an open micro-data set of geo-referenced dwelling listings. The data have been provided by the Idealista company\footnote{Idealista is the major real estate listing website in Spain, and present in other southern european countries as Italy and Portugal} and contain information about 189,923 dwellings located in Spain’s three largest cities. To date, this data product is the biggest open geo-referenced micro-data set of the housing market in Spain. Moreover, the data set has been supplied directly by Idealista, and therefore is clean and free of download errors. The listings have been enriched with official information from the Spanish cadastre along with other relevant geographical features, such as distance to urban points of interest. The data set is distributed as an R package, named ‘idealista18’, which can be accessed from the Github repository.

@@

>>>>

---
title: A geo-referenced micro-data set of real estate listings for Spain’s three largest cities
runninghead: author \emph{et al}.
author:
- name: 
abstract: "This article shares an open data product with big geo-referenced micro-data sets of 2018 real estate listings in Spain. These data were originally published on the idealista.com real estate website. The observations were obtained for the three largest cities in Spain: Madrid (n = 94,815 observations), Barcelona (n = 61,486 observations), and Valencia (n = 33,622 observations). The data sets include the coordinates of properties (latitude and longitude), asking prices of each listed dwelling, and several variables of indoor characteristics. The listings were enriched with official information from the Spanish cadastre (e.g., building material quality) plus other relevant geographical features, such as distance to urban points of interest. Along with the real estate listings, the data product also includes neighborhood boundaries for each city. The data product is offered as a fully documented R package and is available for scientific and educational purposes, particularly for geo-spatial studies"

@@

We are also witnessing a growing interest in open data in geography and data science [@arribasl2021editorial; @arribas2021] using reproducible or replicable  research  [@paez2021open; @brunsdon2021opening]. But  to  work  openly in  science, it  is  necessary to  have  free software and open data. While great efforts have been made to make free software available to researchers (e.g., R or Python), data regarding real estate markets tend to be treated as confidential, and there are still few open micro-data sets of housing markets available [@Song2021].

To contribute to the growing inventory of international micro-data sets of real estate markets, this paper introduces an open micro-data set of geo-referenced dwelling listings. The data have been provided by the Idealista company\footnote{Idealista is the major real estate listing website in Spain, and present in other southern european countries as Italy and Portugal} and contain information about 189,923 dwellings located in Spain’s three largest cities. To date, this data product is the biggest open geo-referenced micro-data set of the housing market in Spain. Moreover, the data set has been supplied directly by Idealista, and therefore is clean and free of download errors. However, in order to be able to share publicly the data we have slightly modified some variables by applying some random noise which will not bias the main results derived from its usage.

This micro-data set is expected to be used as a benchmark dataset to test empirical methods in a reproducible fashion. Applied and theoretical researchers on real estate mass appraisal and valuation methods might use this dataset to canonically compare the performance of their proposed comparable and hedonic models, among others. The data can also be used to study the segmentation of housing submarkets and related topics such as the impact of suburban areas on house prices. The listings have been enriched with official information from the Spanish cadastre along with other relevant geographical features, such as distance to urban points of interest. In any case, the data might be easily extended by spatially joining other datasets that contain information at administrative, census tract, or postal code levels.

The data set is distributed as an R package, name {idealista18}, which can be accessed from a public Github repository\footnote{The direct URL to the GitHub repository is \url{https://github.com/paezha/idealista18}}. The database idealista18 is made available under the \href{http://opendatacommons.org/licenses/odbl/1.0/}{Open Database License}. For transparency, we also share the randomisation process applied to the original data in the aforementioned Github repository.

<!-- @cohen2008spatial (508 observations) -->
<!-- @lazrak2014market (19000 observations) -->

@@

# Declaration of Competing Interest

Author One and author Two are employed by Idealista. They have been granted permission to share the data presented in this article. None of the authors have financial interests or personal relationships which have, or could be perceived to have, influenced the work reported in this article.

# Acknowledgments

The authors wish to thank Alessandro Galesi for their support in the paper revision and Juan Ramón Selva for collecting and cleaning the spatial data. This work has been partially funded by the Spanish Ministry of Economy and Competitiveness Grants PID2019-107800GB-100
